\documentclass[11pt, a4paper]{article} % Document font size and paper size
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{verse} % Required for typesetting poems - this package drives this template
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{xcolor}
\usepackage{pagecolor}
\usepackage[normalem]{ulem}

\usepackage{palatino} % Use the Palatino font by default
%\usepackage{stix} % Alternative Stix font
\setlength{\parindent}{0pt} % Disable paragraph indentation
% Author styles
\newcommand{\poemauthorcenter}[1]{\nopagebreak{\centering\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem center aligned
\newcommand{\poemauthorright}[1]{\nopagebreak{\raggedleft\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem aligned right
\renewcommand{\poemtitlefont}{\normalfont\bfseries\large\centering} % Define the poem title style
\setlength{\stanzaskip}{0.75\baselineskip} % The distance between stanzas
\pagestyle{empty} % Stop page numbering through the document
%\pagecolor{yellow!30!orange}
\pagecolor{Tan!30!white}


%%


% new LaTeX commands
\newfont{\letterbeta}{yinit.tfm}

\begin{document}
{\letterbeta Z}
\poemtitle{}

\settowidth{\versewidth}{Never coudve been less certain but more lucid about it} % Insert one of the average-sized verses, used for centering the poem

\begin{verse}[\versewidth]
{\scriptsize 

%------------------------------------------------

Never coud've been less certain but more lucid about it, \\
yet still, one might wonder kowning the full still on it. \\
who, we. \\
Waajacu: an athemh to descrive common knowledge together. \\
to acomulatte tradition way of sharred manner in knowing. \\
to know still a way to drive feeling, host it preciscly put on the non conflict regime asgiment of discret infinite symbols. ---and growit behond it, it's hope is to acline tought; meaning, to know a bast source for abrastract human descriptive tought that is not explicit, to order the description of all defined human procedures; and guide explicit practice of the tols behind the building of knowledge, aquired and sharred commusism ---otherwise there is conflict.\\
poetry is the Hope to never divided reasons; \\
for still, as laws is play in shared symbols. \\
on the common builded mechanics for symbols lies all practices, so again by the no introduction conflict conduct of Waajacu we must share non a determined way of meaning or rendering visual abrastract: The mechanics to the symbols not the symbols. \\!



%------------------------------------------------
}
\end{verse}

%------------------------------------------------

\poemauthorright{waajacu open source fundation.} % Right-aligned author

%----------------------------------------------------------------------------------------


\end{document}
