\documentclass[11pt, a4paper]{article} % Document font size and paper size
\usepackage[dvipsnames,svgnames,table]{xcolor}
\usepackage{verse} % Required for typesetting poems - this package drives this template
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{xcolor}
\usepackage{pagecolor}
\usepackage[normalem]{ulem}

\usepackage{palatino} % Use the Palatino font by default
%\usepackage{stix} % Alternative Stix font
\setlength{\parindent}{0pt} % Disable paragraph indentation
% Author styles
\newcommand{\poemauthorcenter}[1]{\nopagebreak{\centering\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem center aligned
\newcommand{\poemauthorright}[1]{\nopagebreak{\raggedleft\footnotesize\textsc{#1}\par}} % Author as a footnote at the end of the poem aligned right
\renewcommand{\poemtitlefont}{\normalfont\bfseries\large\centering} % Define the poem title style
\newcommand\tab[1][1cm]{\hspace*{#1}}
\setlength{\stanzaskip}{0.75\baselineskip} % The distance between stanzas
\pagestyle{empty} % Stop page numbering through the document
%\pagecolor{yellow!30!orange}
\pagecolor{Tan!30!white}


%%


% new LaTeX commands
\newfont{\letterbeta}{yinit.tfm}

\begin{document}

{\letterbeta}.


\poemtitle{}

\settowidth{\versewidth}{DULCE DICHA OCULTA DE LOS QUE SE REBELAN SÓLOS } % Insert one of the average-sized verses, used for centering the poem

\begin{verse}[\versewidth]
{\scriptsize

%------------------------------------------------

terminar... 

%------------------------------------------------

Quise ser por siempre viejo y había un buen plan, \\
pero se fabricó la idea del rifle. \\!

%------------------------------------------------

Pandora la esperanza que hay en los números. \\
Las criaturas pensaron necesaria gobernar la sagrada paz; \\
El sudor del gris, invita a negociar sin fuerza. \\!

No se olvida el tao lo que hay en los Números, \\
tanto como es sagrada la idea de Galaxia, es la fidelidad de la Máquina. \\

%------------------------------------------------


%------------------------------------------------



so let's say one wants to write to the science community; \\
no name, i'm to stupid to pool one like it. \\
---diferential eliptic curves of "zero knowledge". --like on knowledge but to find 'zero conflict'. \\
---id sugest we coexist for a chance the practia of non-conflict whatsoever, \\
If we quant conflict on a no giving knowledge framework, just; \\
Let us agree for now, one is avobe nature. And that i'm avobe below on practice to beat respect enough or science about 
a matter that behave as nature. \\!

i need to gfinish and change title....

by an axiomatic eliptical metric formula to quant a statement of interest with out givin away information. \\
---there is too much to work on, and hope not be given. \\

For a science in a shell, the abandonment of chances duels rushing. \\
Let me not be cheap in science; show me the dao. \\

}
\end{verse}

%------------------------------------------------

\poemauthorright{FUNDACIÓN DE FUENTE LIBRE WAAJACU} % Right-aligned author

%----------------------------------------------------------------------------------------


\end{document}
